### 2020-02-08 cv_models.tex
updated main sections

\paragraph{Average Quality Metrics versus Reported Test Accuracies.}
We have examined the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
To start, Figure~\ref{fig:vgg-metrics} considers the VGG series (in particular, the pretrained models VGG11, VGG13, VGG16, and VGG19, with and without BatchNormalization), and it plots the four quality metrics versus the reported Test accuracies~\cite{pyTorchVgg}, as well as a basic linear regression line. 
%with the Root Mean Squared Error (RMSE) shown, \michael{XXX.  WHERE IS RMSE.  IN THAT TABLE?}
All four metrics correlate quite well with the reported Top1 Accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalziation (i.e., greater accuracy, lower error). 
While all four metrics perform well, notice that the Log $\alpha$-Norm metric ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) performs best (with an RMSE of $0.42$, see Table~\ref{table:cv-models}); and the Weighted Alpha metric ($\hat\alpha =\alpha\log\lambda_{max} $), which is an approximation to the Log $\alpha$-Norm metric~\cite{MM20_unpub_work}, performs second best (with an RMSE of $0.48$, see Table~\ref{table:cv-models}).

\begin{figure}[t]
    \centering
    \subfigure[ Frobenius Norm, VGG ]{
        %\includegraphics[width=5cm]{img/VGG_lognorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    %\qquad
    \subfigure[ Spectral Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    %\qquad
    \subfigure[ Weighted Alpha, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    %\qquad
    \subfigure[ $\alpha$-Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of average log Norm empirical quality metrics versus reported test accuracy for pretrained VGG models (with and without BatchNormalization), trained on ImageNet, available in pyTorch (v1.x).  Metrics fit by linear regression, RMSE reported. }
    \label{fig:vgg-metrics}
\end{figure}

@@

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
%\begin{tabular}{|l|c|c|c|c|c|}
\hline
 Series    &\#   & $\log\langle\Vert\mathbf{W}\Vert_{F}\rangle$ & $\log\langle\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\log\langle\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 VGG       &  6 & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
 ResNet    &  5 & 0.9  & 1.4  & \textbf{0.61} & 0.66           \\
 ResNet-1K & 19 & 2.4  & 3.6  & \textbf{1.8}  & 1.9            \\
 DenseNet  &  4 & 0.3  & 0.26 & \textbf{0.16} & 0.21           \\
\hline
\end{tabular}
\end{center}
\caption{RMSE (smaller is better) for linear fits of quality metrics to Reported Top1 Test Error for pretrained models in each architecture series.  VGG, ResNet, and DenseNet were pretrained on ImageNet, and ResNet-1K was pretrained on ImageNet-1K. 
\michael{double check numbers}
}
\label{table:cv-models}
\end{table}

@@

\paragraph{Correlation Flow}
We can learn much more about a pretrained model by going beyond average values to examining quality metrics for each layer weight matrix, $\mathbf{W}$, as a function of depth (or layer id).  % in the network. 
%The most interesting results are seen when we 
For example, we can 
plot (just) the PL exponent, $\alpha$,%
\footnote{That is, here we consider just $\alpha$ for each layer, i.e., not $\hat{\alpha}$ or $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}$.} 
as a function of depth.
%
See Figure~\ref{fig:3models-alpha-layers}, which plots $\alpha$ for each layer (the first layer corresponds to data, the last layer to labels) for the least accurate (shallowest) and most accurate (deepest) model in each of the VGG (without BatchNormalization), ResNet-1K, and DenseNet series.
(Again, much more detailed set of plots is available at \cite{XXX-WEB-LINK}; but note that the corresponding layer-wise plots for Frobenius and Spectral norms are much less interesting than the results we present here.)

>>>>

\paragraph{Average Quality Metrics versus Reported Test Accuracies.}
We have examined the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
To start, Figure~\ref{fig:vgg-metrics} considers the VGG series (in particular, the pretrained models VGG11, VGG13, VGG16, and VGG19, with and without Batch Normalization), and it plots the four quality metrics versus the reported Test accuracies~\cite{pyTorchVgg}, as well as a basic linear regression line. 
%with the Root Mean Squared Error (RMSE) shown, \michael{XXX.  WHERE IS RMSE.  IN THAT TABLE?}
All four metrics correlate quite well with the reported Top1 Accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalziation (i.e., greater accuracy, lower error). 
While all four metrics perform well, notice that the Log $\alpha$-Norm metric ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) performs best (with an RMSE of $0.42$, see Table~\ref{table:cv-models}); and the Weighted Alpha metric ($\hat\alpha =\alpha\log\lambda_{max} $), which is an approximation to the Log $\alpha$-Norm metric~\cite{MM20_unpub_work}, performs second best (with an RMSE of $0.48$, see Table~\ref{table:cv-models}).

\begin{figure}[t]
    \centering
    \subfigure[ Frobenius Norm, VGG ]{
        %\includegraphics[width=5cm]{img/VGG_lognorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    %\qquad
    \subfigure[ Spectral Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    %\qquad
    \subfigure[ Weighted Alpha, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    %\qquad
    \subfigure[ $\alpha$-Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        \includegraphics[width=4.0cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of average log Norm empirical quality metrics versus reported test accuracy for pretrained VGG models (with and without Batch Normalization (BN)), trained on ImageNet, available in pyTorch (v1.x).  Metrics fit by linear regression, RMSE reported. }
    \label{fig:vgg-metrics}
\end{figure}

@@

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
%\begin{tabular}{|l|c|c|c|c|c|}
\hline
 Series    &\#   & $\log\langle\Vert\mathbf{W}\Vert_{F}\rangle$ & $\log\langle\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\log\langle\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 VGG       &  6 & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
 ResNet    &  5 & 0.9  & 1.4  & \textbf{0.61} & 0.66           \\
 ResNet-1K & 19 & 2.4  & 3.6  & \textbf{1.8}  & 1.9            \\
 DenseNet  &  4 & 0.3  & 0.26 & \textbf{0.16} & 0.21           \\
\hline
\end{tabular}
\end{center}
\caption{RMSE (smaller is better) for linear fits of quality metrics to Reported Top1 Test Error for pretrained models in each architecture series.  VGG, ResNet, and DenseNet were pretrained on ImageNet, and ResNet-1K was pretrained on ImageNet-1K. 
}
\label{table:cv-models}
\end{table}

@@

\paragraph{Correlation Flow}
We can learn much more about a pretrained model by going beyond average values to examining quality metrics for each layer weight matrix, $\mathbf{W}$, as a function of depth (or layer id).  % in the network. 
%The most interesting results are seen when we 
For example, we can 
plot (just) the PL exponent, $\alpha$,%
\footnote{That is, here we consider just $\alpha$ for each layer, i.e., not $\hat{\alpha}$ or $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}$.} 
as a function of depth.
%
See Figure~\ref{fig:3models-alpha-layers}, which plots $\alpha$ for each layer (the first layer corresponds to data, the last layer to labels) for the least accurate (shallowest) and most accurate (deepest) model in each of the VGG (no BN), ResNet, and DenseNet series.
(Again, much more detailed set of plots is available at \cite{XXX-WEB-LINK}; but note that the corresponding layer-wise plots for Frobenius and Spectral norms are much less interesting than the results we present here.)
